### 2020-06-25 manuscript/manuscript.rmd
small tweak

We parsed the `r nrow(analyses_published)` previous phylogenetic analyses from `r length(unique(analyses_published$manuscript))` studies (Fig. 3A and Supplementary Table 2). Among these studies, the main conclusions of five studies strongly favor of Porifera-sister and 10 favor Ctenophora-sister (Extended Data Table 1). Three studies are based entirely on previously published data, and the remainder add data for one or more species.

All published analyses that use models with site-homogeneous equilibrium frequencies (*i.e.*, models that do not include CAT) strongly support Ctenophora-sister, regardless of other factors such as outgroup choice (Fig. 3A). Some analyses that exclude more distant outgroups and use models with site-heterogeneious CAT equilibrium frequencies support Porifera-sister. Because CAT is so parameter rich, many analyses that use a CAT model do not converge, and some of the unconvered analyses have an unresolved animal root. The strong support of Porifera-sister can only be recovered from analyses analyses of protein sequences using Poisson+CAT. Although GTR+CAT model generally has better model adequacy than Poisson+CAT or site-homogeneous models from previous studies[@pisani2015genomic; @feuda2017improved], Porifera-sister is not always supported since several analyses strongly in favor Ctenophora-sister even with only choanofalgellates are used as outgroups (Fig. 3A). Thus, our summary of previous phylogenetic analyses strongly indicated that the trend of the support of Porifera-sister is generally increasing with the use of more complex CAT models and more closely related outgroups in several representative matrices, whereas Ctenophora-sister is supported in most other conditions.

>>>>

We parsed `r nrow(analyses_published)` previous phylogenetic analyses from `r length(unique(analyses_published$manuscript))` studies (Fig. 3A and Supplementary Table 2). The conclusions of five studies strongly favor of Porifera-sister and 10 favor Ctenophora-sister (Extended Data Table 1). Three studies are based entirely on previously published data, and the remainder add data for one or more species.

All published analyses that use models with site-homogeneous equilibrium frequencies (*i.e.*, models that do not include CAT) strongly support Ctenophora-sister, regardless of other factors such as outgroup choice (Fig. 3A). Some analyses that exclude more distant outgroups and use models with site-heterogeneious CAT equilibrium frequencies support Porifera-sister. Because CAT is so parameter rich, many analyses that use a CAT model do not converge, and some of the unconvered analyses have an unresolved animal root. Although model adequacy assessments generally favor GTR+CAT over Poisson+CAT or site-homogeneous models [@pisani2015genomic; @feuda2017improved], Porifera-sister is not always supported since several analyses strongly in favor Ctenophora-sister even with only choanofalgellates are used as outgroups (Fig. 3A). Thus, our summary of previous phylogenetic analyses strongly indicated that the trend of the support of Porifera-sister is generally increasing with the use of more complex CAT models and more closely related outgroups in several representative matrices, whereas Ctenophora-sister is supported in most other conditions.
